Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-02-26 manuscripts/paper-1/main.tex
PreCorrection

    \subsection{Research question}\label{section: Research Questions}
    What is the quality of digital twins?

@@

    \section{Initial approach in the FELICE project}
    Inspired by ISO 25010...

@@

    \subsubsection{Findings from FELICE}
    TODO

@@

    \subsubsection{Findings from FELICE}
    TODO

    \section{Future approach in the FELICE project}
    \label{section:framework_1}
    TODO

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Digital Twin Deviation.png}
        \caption{TODO}
        \label{todo-2}
    \end{figure}

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Digital Twin.png}
        \caption{TODO}
        \label{todo-1}
    \end{figure}

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Continuous Quality Control.png}
        \caption{TODO}
        \label{todo-3}
    \end{figure}

    \section{Conclusion}~\label{section:conclusion}
    TODO

    \section*{Acknowledgements}
    TODO

>>>>

    \subsection{Research question}\label{section: Research Questions}
    What is the quality of digital twins?
    What is the state art of digital twin quality?

@@

    \section{Initial approach in the FELICE project}
    FELICE addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting. This challenge requires the development of sophisticated algorithms and techniques that facilitate seamless communication, 
    cooperation, and coordination between humans and robotic agents. By addressing this issue, FELICE tries to represent a 
    significant advancement in the field of robotics and has the potential to enhance the effectiveness and efficiency of a wide range of human-robot collaborative tasks with the consideration of safety~\cite{FELICE}.

    In the present study, we inspected several artifacts to evaluate the quality of the digital twin for the FELICE project, which is currently in the design phase. These artifacts included process videos showing the current assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, 
    and a discrete event simulation module. We assessed the quality of these artifacts based on four crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.

@@

@@

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{quality_inspection_results.png}
        \caption{Overall Quality Inspection Results}
        \label{fig:QualityInspectonResults}

    \end{figure}\begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{quality_inspection_results_with_artifacts.png}
        \caption{ Quality Inspection Results Categorized with Artifacts}
        \label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}

    As can be seen in Figures ~\ref{fig:QualityInspectonResults} and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
    we have identified a total of seven correctness issues, eleven completeness issues, and two fidelity issues. 
    It is important to note that we were unable to inspect for efficiency as the project is still in the design phase, 
    and we do not have enough data to make estimations for this attribute. Additionally, all of our inspections were conducted manually, 
    which is susceptible to human error and inspector bias.

    \subsection{Future approach in the FELICE project}
    \label{section:framework_1}
    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation. As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins. Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments. 
    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.

    \section{Conclusion}~\label{section:conclusion}
    The success of the digital twin system depends on its quality, which requires careful evaluation based on several crucial quality attributes. The correctness of the system is measured by how accurately it behaves compared to the real system.
    Completeness assesses whether the digital twin's subsystems and relations match those of the real system. 
    Fidelity refers to the degree of exactness with which the real system is copied and represented.
    Efficiency measures the productivity of the system and the minimum waste during the process. 
    Evolvability is the system's ability to enhance its suitability to its environment through alterations to both its internal and functional structure. 
    Evaluating these quality attributes of the FELICE digital twin system will help ensure its success in effectively integrating human and robot abilities in a collaborative setting, leading to enhanced efficiency and safety in various human-robot collaborative tasks.
    \section*{Acknowledgements}
    TODO
